%%%& -job-name=CV_Andres_Navarrete
\documentclass[11pt,letterpaper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking' and 'fancy'
\moderncvcolor{purple}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.85,letterpaper]{geometry}
\usepackage{babel}
\usepackage{fontawesome}

%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Andrés}
\familyname{Navarrete Contardo}
%\title{Curriculum Vitae}                               
\address{Santiago, Chile}  %\address{street and number}{postcode city}{country}      
\phone[mobile]{+56 9 85897103}                          
                  
%\homepage{www.johndoe.com}
\social[linkedin]{andresnavarretecontardo}
\social[github]{AndresNavarrete}
\email{ainavarrete@uc.cl}
%\email{a.navarrete.contardo@gmail.com}

% \photo[64pt][0.4pt]{picture}                

% \quote{
% Civil Industrial Engineer in Transportation // Logistics and Operations Research | Professional experience in logistics and operational and strategic consulting.
% }

\begin{document}
\makecvtitle
\section{Professional Experience}

\cventry{2023 - Present}{\href{https://www.linkedin.com/company/metro-de-santiago-s-a-/}{Metro de Santiago}}{}{}{}{
\begin{description}
\item [Data Scientist] Responsible for analyzing and interpreting large volumes of data to support strategic decisions within the organization. I develop analytical and predictive models using statistical and Machine Learning techniques. I manage databases, automate reports, and optimize processes through the integration of data from multiple systems. My role also includes creating visualizations and generating actionable insights that help improve operational efficiency and enhance the user experience.
\end{description}
}

\cventry{2021 - 2023}{\href{https://www.linkedin.com/company/dispatchtrack-es/}{Beetrack - DispatchTrack}}{}{}{}{
\begin{description}
\item [Data Engineer (2022 - 2023)] I executed data engineering and analysis projects, designing solutions for process automation and extracting value from large volumes of information. Key achievements:
\begin{itemize}
\item Designed and implemented integrations between commercial, financial, and operational systems, managing the corporate Datawarehouse and overseeing the data transfer infrastructure.
\item Created visibility of key metrics through automated reports in Tableau, integrated with tools such as Hubspot and Intercom, to prevent customer churn.
\item Implemented predictive models for customer segmentation and behavior analysis, ensuring autonomous operation in production with MLOps practices.
\end{itemize}
\item [Project Engineer (2021)] Developer in the product team, focused on creating technological solutions to optimize logistics operations. Key projects:
\begin{itemize}
\item Designed and programmed algorithms for fleet routing, reducing costs and increasing operational efficiency, as well as an inventory management model that optimized costs in high-turnover industries.
\item Built a predictive service using artificial intelligence to estimate travel times considering traffic conditions, improving planning and decision-making in logistics operations.
\end{itemize}
\end{description}
}

\cventry{2020 - 2021}{\href{https://www.dictuc.cl/}{Dictuc}}{}{}{}{
\begin{description}
\item [Project Engineer] As a consultant in transportation demand studies for the Inter-American Development Bank, I was responsible for designing and implementing mobility surveys in Santiago and Bogotá, as well as analyzing big data and calibrating statistical models to estimate transportation demand. I also developed studies that contributed to a better understanding of mobility patterns in Latin America and the Caribbean. \href{https://blogs.iadb.org/transporte/es/por-que-en-america-latina-y-el-caribe-usamos-tanto-el-automovil/}{See study here}.
\end{description}
}

\section{Education}
\cventry{2018 - 2020}{Master's in Engineering Sciences}{Pontificia Universidad Católica de Chile}{}{}{Thesis in the Department of Transportation and Logistics Engineering: \textit{Efficient planning of a home delivery operation integrated with public transport services}. \href{https://repositorio.uc.cl/xmlui/handle/11534/65009}{\textbf{See thesis here.}}}{} 

\cventry{2013 - 2019}{Civil Industrial Engineering}{PUC}{}{}{Diploma in Transportation Engineering.}

\cventry{2013 - 2016}{Bachelor of Natural Sciences and Mathematics}{PUC}{College UC}{}{Major: Operations Research. Minor: Human Resources \& Transportation Systems.}

\newpage

\subsection{Professional Development}
\cventry{}{Certifications}{}{}{}{
    \begin{itemize}
        \item Advanced Tableau for Data Science. \href{https://www.udemy.com/certificate/UC-1467d971-22b4-47fc-9e4e-f8ee401bbb0d/}{\textbf{See certificate on Udemy}}
		\item Machine Learning Algorithms applied in Python and R. \href{https://www.udemy.com/certificate/UC-33369609-4adb-45a7-b550-d2e5d252a04c/}{\textbf{See certificate on Udemy}}
		\item Applied Apache Airflow course. \href{https://www.udemy.com/certificate/UC-af5ee666-1176-4f27-a834-7b7cf699eee8/}{\textbf{See certificate on Udemy}}
		\item Machine Learning applied to AWS platforms and services. \href{http://www.coursera.org/verify/VHZPPXDH7N3N}{\textbf{See certificate on Coursera}}
		\item Google Analytics 4 Certification. \href{https://skillshop.exceedlms.com/student/award/MhNWrQWjRLbmND5DzQhp7X4p}{\textbf{See certificate on Google}}
	\end{itemize}
}

\section{Academic Experience}
\cventry{2020}{Speaker at Conferences}{}{}{}{Speaker at the IV Congress of Engineering Students USM-UC, held from August 27 to 28, 2020.}

\cventry{2015-2019}{Teaching Assistant}{Faculty of Engineering}{PUC}{}{\begin{itemize}
		\item Master's in Industrial Engineering: Simulation Models
		\item Industrial Engineering and Systems: Optimization, Stochastic Models, Simulation, Operations Research Capstone (4 times) and Operations Management.
		\item Transportation and Logistics Engineering: Network Flow
		\item Courses in English: Research, Innovation, and Entrepreneurship.
	\end{itemize}}
\cventry{2015-2017}{Teaching Assistant}{Faculty of Mathematics}{Pontificia Universidad Católica de Chile}{}{Algebra, Calculus I, II, III, and Differential Equations}

\section{Volunteer Work}
\cventry{2021-2023}{Academic Tutor}{Formando Chile}{}{}{Academic tutor for first-year higher education students. I teach classes and provide support in mathematics and programming courses.}

\cventry{2014-2018}{Teacher and Coordinator}{PrePreu}{}{}{General Coordinator of a social education project with over 170 students from vulnerable schools in the Metropolitan Region. I taught for five years and was the general coordinator for two years. Managed a team of over 50 volunteer teachers.}

\cventry{2016-2019}{Academic Tutor}{College UC}{}{}{Academic support and follow-up for students in special admission programs.}

\section{Awards}
\cventry{2017}{100 Young Leaders}{El Mercurio: "El Sábado" magazine, Universidad Adolfo Ibáñez}{}{}{Recognition for a project on innovation in firefighter and rescue team safety in Chile. This award is given annually to 100 Chileans under 35 years old who are seen as potential leaders for the country.}{}{}
\cventry{2017}{Finalist, Global Student Entrepreneurship Challenge}{Virginia Tech}{Virginia, USA}{}{Finalist in an international university entrepreneurship competition.}
\cventry{2017}{Best Student of the 2017 Cohort}{College UC}{Bachelor's in Natural Sciences and Mathematics}{}{Student with the highest grade.}

\section{Technical Skills}
\cvitemwithcomment{English}{C1. 99 in TOEFL IBT, October 2019}{}
\cvitemwithcomment{Technologies}{Python, Linux, AWS, R, Kotlin, Gurobi, Latex}{ \href{https://github.com/AndresNavarrete}{\textbf{See portfolio on GitHub}}  }
%\section{References}
  % available upon request

\end{document}
